---
title: "Practical Machine Learning Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data

The training data for this project are available here:
<https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv>

The test data are available here:
<https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv>

Load the data:
```{r}
options(stringsAsFactors = FALSE)
training <- read.csv("~/Dropbox/coursera/PracticalMachineLearning/assignment/pml-training.csv")
```
How to deal with missing values? If we use use 'complete.cases' - no removes 95% of the data!  So let's remove fields where > 90% empty, timestamps, 'X':
```{r}
idx <- which(colSums(is.na(training))/nrow(training) > 0.9)
idx <- c(idx, which(sapply(training, function(x) sum(x==""))/nrow(training) > 0.9))
idx <- c(idx, which(grepl("timestamp", names(training))))
idx <- c(1, idx)
idx <- sort(unname(idx))

training <- training[,-idx]

training$user_name <- as.factor(training$user_name)
training$new_window <- as.factor(training$new_window)
training$classe <- as.factor(training$classe)
```
Random Forests are easy to run in parallel:
```{r}
library(doMC)
registerDoMC(2)
```
Load the 'caret' package and train the Random Forest:
```{r}
library(caret)
modRF <- train(classe ~ ., data=training, method="parRF")
summary(modRF)
```

Load the testing data and format to be the same as the training data:
```{r}
testing <- read.csv("~/Dropbox/coursera/PracticalMachineLearning/assignment/pml-testing.csv")
testing <- testing[,-idx]

testing$user_name <- factor(testing$user_name, levels = levels(training$user_name))
testing$new_window <- factor(testing$new_window, levels = levels(training$new_window))

testing <- testing[,-which(names(testing)=="problem_id")]

predTest <- predict(modRF, newdata=testing)
print(predTest)
```